Quantifying the manageability of pollination networks in an invasion context

### 2017-02-28 paper/draft_2.Rmd
Change to submission formating

---
title: "Quantifying the manageability of pollination networks in an invasion context"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption} 
- \usepackage{lineno}
documentclass: artikel1
bibliography: references.bib
---

\doublespacing
\linenumbers

>>>>

---
title: "Quantifying the manageability of pollination networks in an invasion context"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
    includes:
      after_body: after_body.md
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{tocloft} 
- \usepackage{caption}
- \captionsetup{labelsep=none,textformat=empty}
- \usepackage{lineno}
- \usepackage[nomarkers,tablesfirst, nolists]{endfloat}
- \cftpagenumbersoff{figure}
- \cftpagenumbersoff{table}
documentclass: artikel1
bibliography: references.bib
---

\doublespacing
\linenumbers
\renewcommand*\listfigurename{Figure legends}
\renewcommand*\listtablename{Table legends}
